At the outset, we must thank Leo Laine\footnote{Chassis Strategies and Vehicle Analysis, Volvo Group Trucks Technology SE}, for his watchful guidance, encouragement and insight. His unbounding enthusiasm and ease has, on more occasion than one, lent newer dimensions to our reasoning and research. Thanks are also due to Peter Lindroth\textsuperscript{1}\footnote{Chassis Strategies and Vehicle Analysis, Volvo Group Trucks Technology SE}, for his keen observations and direction that were instrumental in defining the optimisation goals succinctly and in developing the genotype-phenotype translations, in specific. We must express our gratitude to\\

Dr. Jonas Hellgren\footnote{Advanced Technology and Research, Volvo Group Trucks Technology SE}, whose research formed the basis of our thesis,\\ 

Prof. Mattias Wahde\footnote{Vehicle Engineering and Autonomous Systems, Chalmers University of Technology SE}, for his inspiring lectures on evolutionary algorithms,\\

Ola Benderius\footnote{Vehicle Engineering and Autonomous Systems, Chalmers University of Technology SE}, whose support in structuring the genetic algorithm and its programming was nonpareil,\\ 

Balaji Rao\footnote{Indian Institute of Science, IN}, for his masterly suggestions on the software architecture and its implementation\\

Prof. Bengt Jacobson\footnote{Vehicle Engineering and Autonomous Systems, Chalmers University of Technology SE}, Niklas Fr\"ojd\footnote{Chassis Strategies and Vehicle Analysis, Volvo Group Trucks Technology SE} and Lars Wallin\footnote{Chalmers University of Technology SE}, for sparing time to discuss the vehicle model, and\\

Dr. Bal\'azs Adam Kulcs\'ar\footnote{Signals and Systems, Chalmers University of Technology SE}, for sharing his thoughts on the optimal predictive cruise controller\\

Stefan Edlund\footnote{Chief Engineer, Chassis Strategies and Vehicle Analysis, Volvo Group Trucks Technology SE} and Inge Johansson\footnote{Group Manager, Chassis Strategies and Vehicle Analysis, Volvo Group Trucks Technology SE}, along with the team at Volvo have been very supportive and gracious hosts to us over the duration of the thesis research. Our thanks to them too.\\

Special mention must be made of Jan Schr\"oder, Daniela Holzner, Syarifah Siregar and Niels van Duijkeren, whose constant company at Volvo made research more fun, code debugging bearable and the fika sessions memorable.\\

Karthik Venkataraman and Nikhil Acharya